Model LF

### 2022-10-29 Final test.Rmd
Commit lf kanal tilføjet

@@

@@

@@

>>>>

 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

## Baseline Scenario 7b

```{r}
# Define add-factor list (defining shock)
constantAdjList_bs7b <- list(

```{r}
# Simulate the model (following shock)
Shock_bs7b <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_bs7b
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_bs7b = Shock_bs7b$simulation$max_dp
wage_bs7b = Shock_bs7b$simulation$wage
komp_r_bs7b = Shock_bs7b$simulation$komp_r
part_bs7b = Shock_bs7b$simulation$part
yk_ds_bs7b = Shock_bs7b$simulation$yk_ds
pc_ds_bs7b = Shock_bs7b$simulation$pc_ds
wage_ds_t_bs7b = Shock_bs7b$simulation$wage_ds_t
ur_ds_bs7b = Shock_bs7b$simulation$ur_ds
emp_bs7b = Shock_bs7b$simulation$emp
yd_hk_ds_bs7b = Shock_bs7b$simulation$yd_hk_ds

tilpas_pr_bs7b = Shock_bs7b$simulation$tilpas_pr
u_ds_bs7b = Shock_bs7b$simulation$u_ds
part_bs7b = Shock_bs7b$simulation$part
nben_h_bs7b = Shock_bs7b$simulation$nben_h
wage_ds_bs7b = Shock_bs7b$simulation$wage_ds
dp_person_bs7b = Shock_bs7b$simulation$dp_person
kont_h_ratio_bs7b = Shock_bs7b$simulation$kont_h_ratio

nl_g_bs7b = Shock_bs7b$simulation$nl_g
unemp_bs7b = Shock_bs7b$simulation$unemp
yd_hk_ds_bs7b = Shock_bs7b$simulation$yd_hk_ds
wage_gap1_bs7b = Shock_bs7b$simulation$wage_gap1
wage_gap_bs7b = Shock_bs7b$simulation$wage_gap
prod_bs7b = Shock_bs7b$simulation$prod
```

@@

  shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

# Scenario 7b All but prod

```{r}
# Define add-factor list (defining shock)
constantAdjList7b <- list(

```{r}
# Simulate the model (following shock)
Shock_7b <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList7b
                    )

yk_ds_07b = Shock_7b$simulation$yk_ds
emp_07b = Shock_7b$simulation$emp
wage_ds_07b= Shock_7b$simulation$wage_ds
ur_ds_07b = Shock_7b$simulation$ur_ds
pc_ds_07b = Shock_7b$simulation$pc_ds
yd_hk_ds_07b = Shock_7b$simulation$yd_hk_ds
pconk_ds_07b = Shock_7b$simulation$pconk_ds
komp_r_07b = Shock_7b$simulation$komp_r
max_dp_07b = Shock_7b$simulation$max_dp
nben_h_07b = Shock_7b$simulation$nben_h
yd_hk_ds_07b = Shock_7b$simulation$yd_hk_ds
ik_07b = Shock_7b$simulation$ik
wage_ds_t_07b = Shock_7b$simulation$wage_ds_t
nben_h_un_07b = Shock_7b$simulation$nben_h_un
nl_g_07b = Shock_7b$simulation$nl_g
nsben_h_07b = Shock_7b$simulation$nsben_h
dp_person_07b = Shock_7b$simulation$dp_person
u_ds_07b = Shock_7b$simulation$u_ds
shock_kuld_07b = Shock_7b$simulation$shock_kuld
unemp_07b = Shock_7b$simulation$unemp

part_07b = Shock_7b$simulation$part
```

```{r}
plot(((emp_07b - emp_bs7b)*1000), col= "blue", xlab= "Year", ylab= "Change in employment (people)", main= "Change in Employment", ylim= c(-5000, 300));
lines(((emp_04 - emp_bs4)*1000), col= "black");
lines(((emp_02 - emp_bs2)*1000), col= "red");
lines(((emp_01 - emp_00)*1000), col= "green");
legend("left", legend=c("All channels except productivity", "insurance rate channel", "wage channel", "demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black","red", "green"));
grid()
```

```{r}
plot(((nl_g_07b - nl_g_bs7b)), col= "blue", xlab= "Year", ylab= "Change in Government net lending", main= "Change in Government net-lending");
lines(((nl_g_04 - nl_g_bs4)), col= "black");
lines(((nl_g_02 - nl_g_bs2)), col= "red");
lines(((nl_g_01 - nl_g_00)), col= "green");
legend("left", legend=c("All channels except productivity", "insurance rate channel", "wage channel", "demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black","red", "green"));
grid()
```

Legend passer ik 
```{r}
plot(((yk_ds_05 - yk_ds_bs56) / yk_ds_bs56), col= "blue", xlab= "Year", ylab= "% Change in Gdp", main= "Gdp", ylim= c(-0.0001, 0.0015));
lines(((yk_ds_04 - yk_ds_bs4) / yk_ds_bs4), col= "yellow");
lines(((yk_ds_07b - yk_ds_bs7b) / yk_ds_bs7b), col= "red");
lines(((yk_ds_03 - yk_ds_bs3) / yk_ds_bs3), col= "black");
lines(((yk_ds_02 - yk_ds_bs2) / yk_ds_bs2), col= "orange");
lines(((yk_ds_01 - yk_ds_00) / yk_ds_00), col= "green");
legend("left", legend=c("All channels","All channels but productivity","Insurance rate channel", "Productivity channel", "Wage channel", "Demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue", "yellow","red", "black","orange", "green"));
grid()
```

```{r}
plot(((emp_06b - emp_bs7b)*1000), col= "blue", xlab= "Year", ylab= "Change in employment (people)", main= "Change in Employment");
lines(((emp_07b - emp_bs7b)*1000), col= "black");
legend("left", legend=c("All channels except productivity", "All channels except productivity"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black"));
grid()
```

```{r}
plot(part_07b, col= "red"); lines(part_bs7b, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```
